\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{hangparas}{0.15in}{1}
\setlength{\parskip}{6pt}

(AAG), American Association of Geographers. \t\textit{The Ethical Challenges of GeoAI}. New York: Unknown Publisher, 2021.

(CSIS), Center for Strategic and International Studies. \t\textit{Leveraging the Commercial Space Sector}. New York: Routledge, 2022.

(EFF), Electronic Frontier Foundation. \t\textit{The Privacy Challenge of Geospatial Big Data}. New York: Cambridge University Press, 2018.

(IFAD), International Fund for Agricultural Development. \t\textit{Mapping for Change}. New York: Unknown Publisher, 2009.

(OCHA), UN Office for the Coordination of Humanitarian Affairs. \t\textit{Data for Humanity}. New York: Unknown Publisher, 2019.

(SIA), Satellite Industry Association. \t\textit{State of the Satellite Industry Report}. New York: Intl. Engineering Consortiu, 2023.

(UN-GGIM), United Nations Committee of Experts on Global Geospatial Information Management. \t\textit{The Integrated Geospatial Information Framework (IGIF)}. New York: UN, 2018.

(UNDP), United Nations Development Programme. \t\textit{Global Commons and the Digital Age}. New York: Unknown Publisher, 2022.

(WRI), World Resources Institute. \t\textit{Predictive Conservation}. New York: Unknown Publisher, 2022.

(WWF), World Wildlife Fund. \t\textit{Technology for Nature}. New York: Unknown Publisher, 2022.

(ZSL), Zoological Society of London. \t\textit{The Pulse of the Planet: Digital Technology for Conservation}. New York: Chicago Zoological Society, 2021.

2025), The Heritage Foundation (Project. \t\textit{Mandate for Leadership: The Conservative Promise}. New York: Unknown Publisher, 2023.

Affairs, Harvard Belfer Center for Science and International. \t\textit{The Geopolitics of Artificial Intelligence}. New York: Unknown Publisher, 2021.

BlackSky. \t\textit{From Pixels to Insights}. New York: Unknown Publisher, 2022.

Blog, Google AI. \t\textit{AI for Social Good: Flood Forecasting}. New York: MDPI, 2022.

Blog, Google AI. \t\textit{Open Buildings: A new, open dataset of building footprints}. New York: Unknown Publisher, 2021.

Bostrom, Nick. \t\textit{Superintelligence: Paths, Dangers, Strategies}. New York: Unknown Publisher, 2014.

Conservancy, The Nature. \t\textit{Conservation in the Digital Age}. New York: Island Press, 2020.

Conservancy, The Nature. \t\textit{Spatial Planning for Conservation}. New York: Springer Science & Business Media, 2018.

Consortium, Conservation AI. \t\textit{Artificial Intelligence and the Future of Conservation}. New York: Cambridge University Press, 2023.

Couldry, Ulises A. Mejias \\& Nick. \t\textit{Data Colonialism}. New York: Unknown Publisher, 2019.

Council, National Research. \t\textit{A Research Agenda for Geographic Information Science}. New York: National Academies Press, 2007.

Crampton, Jeremy W.. \t\textit{The Politics of the Map in the 21st Century}. New York: University of Chicago Press, 2011.

Dangermond, Jack. \t\textit{Esri User Conference Plenary Session}. New York: Unknown Publisher, 2019.

Dangermond, Jack. \t\textit{The Arc of Collaboration}. New York: Unknown Publisher, 2021.

Dangermond, Jack. \t\textit{Web GIS: The Great Enabler}. New York: Unknown Publisher, 2016.

Dangermond, Jack. \t\textit{The Geographic Advantage}. New York: Unknown Publisher, 2015.

DeepMind. \t\textit{Nowcasting the Rain with DeepMind}. New York: Unknown Publisher, 2021.

DeepMind. \t\textit{Towards a Geographic Artificial Intelligence}. New York: Routledge, 2024.

ESRI. \t\textit{GeoAI: The Next Frontier}. New York: Esri Press, 2020.

ESRI. \t\textit{The Science of Where}. New York: ESRI Press, 2018.

ESRI. \t\textit{The Business of GIS}. New York: ESRI, Inc., 2022.

ESRI. \t\textit{Smarter Cities and the Role of GIS}. New York: MDPI, 2021.

ESRI, Autodesk \\&. \t\textit{GIS and BIM: The Digital Convergence}. New York: Taylor & Francis, 2019.

ESRI. \t\textit{The Future of Indoor GIS}. New York: Getting to Know, 2020.

ESRI. \t\textit{Edge Computing in GIS}. New York: Springer, 2023.

ESRI. \t\textit{4D GIS: A New Paradigm}. New York: Esri Press, 2022.

ESRI. \t\textit{AR/VR and the Future of GIS}. New York: Unknown Publisher, 2022.

Economist, The. \t\textit{Who Owns the Sky?}. New York: Unknown Publisher, 2021.

Euroconsult. \t\textit{The Business of Earth Observation}. New York: Springer, 2022.

Forum, World Economic. \t\textit{The New Space Race: A Question of Governance}. New York: Ledizioni, 2021.

Forum, World Economic. \t\textit{The Sentient World: AI and the Future of Governance}. New York: ABHIJEET SARKAR, 2024.

Good, Google AI for Social. \t\textit{AI for Disaster Response}. New York: John Wiley & Sons, 2021.

Google. \t\textit{Google Earth Engine: A Planetary-Scale Platform}. New York: MDPI, 2017.

Google. \t\textit{Earth Engine: Vision and Impact}. New York: Unknown Publisher, 2018.

Gorelick, Noel. \t\textit{Google Earth Engine: A Retrospective}. New York: Food & Agriculture Org., 2020.

Insight), Planet (via acquisition of Orbital. \t\textit{Seeing the Unseen: The Hyperspectral Revolution}. New York: Unknown Publisher, 2023.

Institute, The Alan Turing. \t\textit{Geospatial Ethics in the AI Era}. New York: Springer Nature, 2022.

Institute, Jane Goodall. \t\textit{Scaling Conservation}. New York: Esri Press, 2020.

Institute, Future of Humanity. \t\textit{The Alignment Problem in Geo-AI}. New York: Unknown Publisher, 2023.

International, Amnesty. \t\textit{The Double-Edged Sword of Satellite Transparency}. New York: Unknown Publisher, 2021.

Kitchin, Rob. \t\textit{Critical Data Studies}. New York: Polity, 2014.

Kurgan, Laura. \t\textit{The Commercialization of the View from Nowhere}. New York: Unknown Publisher, 2013.

Markup, The. \t\textit{The Cloud Cartel}. New York: Unknown Publisher, 2022.

Marshall, Will. \t\textit{Planet Labs PBC Blog}. New York: Unknown Publisher, 2020.

McKinsey, Credit Suisse \\&. \t\textit{The State of Conservation Finance}. New York: Unknown Publisher, 2020.

National Academies of Sciences, Engineering, and Medicine. \t\textit{Thriving on Our Changing Planet: A Decadal Strategy for Earth Observation from Space}. New York: Unknown Publisher, 2018.

National Academies of Sciences, Engineering, and Medicine. \t\textit{Review of the Draft 2022-2032 Strategic Plan for the National Plan for Civil Earth Observations}. New York: Nova Science Publishers, 2022.

National Academies of Sciences, Engineering, and Medicine. \t\textit{Open Science by Design: Realizing a Vision for 21st Century Research}. New York: National Academies Press, 2018.

National Academies of Sciences, Engineering, and Medicine. \t\textit{Explainable AI (XAI) for the Geosciences}. New York: Unknown Publisher, 2023.

National Academies of Sciences, Engineering, and Medicine. \t\textit{Reproducibility and Replicability in Science}. New York: National Academies Press, 2019.

National Academies of Sciences, Engineering, and Medicine. \t\textit{A Vision for Earth System Science}. New York: National Academies Press, 2020.

Microsoft. \t\textit{AI for Earth}. New York: John Wiley & Sons, 2018.

Moore, Rebecca. \t\textit{Empowering Global Change Monitoring}. New York: Unknown Publisher, 2019.

Nations, United. \t\textit{A Guide to the Role of Standards in Geospatial Information Management}. New York: UN, 2015.

Nations, United. \t\textit{Geospatial Information for Sustainable Development}. New York: Unknown Publisher, 2017.

Programme, INTERPOL Environmental Crime. \t\textit{Eyes in the Sky, Boots on the Ground}. New York: Unknown Publisher, 2019.

Research, Google. \t\textit{Causal Inference for Geospatial Data}. New York: MIT Press, 2023.

Sources, Various Academic. \t\textit{Counter-Mapping and the Decolonization of GIS}. New York: University of Chicago Press, 2005.

Sources, Various Academic. \t\textit{Decolonizing the Map: A Critical GIS Perspective}. New York: University of Chicago Press, 2010.

Space, Capella. \t\textit{The Power of Persistence}. New York: Unknown Publisher, 2021.

Srnicek, Nick. \t\textit{Platform Capitalism}. New York: John Wiley & Sons, 2016.

Suri, Mary L. Gray and Siddharth. \t\textit{Ghost Work: How to Stop Silicon Valley from Building a New Global Underclass}. New York: HarperCollins, 2019.

Technologies, Maxar. \t\textit{The Geospatial Revolution}. New York: Springer Science & Business Media, 2019.

UN-GGIM. \t\textit{Future trends in geospatial information management: the fifth report of the UN-GGIM}. New York: Unknown Publisher, 2021.

UN-GGIM. \t\textit{Leaving No One Behind}. New York: Unknown Publisher, 2019.

UN-GGIM. \t\textit{The Global Fundamental Geospatial Data Themes}. New York: UN, 2018.

USGS. \t\textit{Landsat's Enduring Legacy}. New York: Unknown Publisher, 2022.

Véliz, Carissa. \t\textit{The Hidden Atlas: Power and Politics in Geodata}. New York: Unknown Publisher, 2021.

Watch, Human Rights. \t\textit{The Smart City and the Surveillance State}. New York: Oxford University Press, 2020.

Zuboff, Shoshana. \t\textit{The Age of Surveillance Capitalism}. New York: PublicAffairs, 2019.

\end{hangparas}

\cleardoublepage

\vfill
\begin{center}
For more information and to purchase this book, please visit our website:
\par\vspace{1em}
NimbleBooks.com
\end{center}
\cleardoublepage
