\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{hangparas}{0.15in}{1}
\setlength{\parskip}{6pt}

(CCC), Computing Community Consortium. \t\textit{A Roadmap for U.S. Robotics - From Internet to Robotics, 2020 Edition}. New York: Unknown Publisher, 2020.

(ESA), European Space Agency. \t\textit{Human and Robotic Exploration - ESA SciSpacE Strategy}. New York: Unknown Publisher, 2017.

(ESA), European Space Agency. \t\textit{In-Orbit Servicing and Assembly}. New York: Unknown Publisher, 2020.

(OSTP), White House Office of Science and Technology Policy. \t\textit{In-Space Servicing, Assembly, and Manufacturing National Strategy}. New York: National Academies Press, 2022.

Fong, Terry. \t\textit{The Future of Space Robotics and Autonomy (Presentation)}. New York: IET, 2018.

National Academies of Sciences, Engineering, and Medicine. \t\textit{Origins, Worlds, and Life: A Decadal Strategy for Planetary Science and Astrobiology 2023-2032}. New York: Unknown Publisher, 2022.

Murphy, Robin R.. \t\textit{Introduction to AI Robotics, Second Edition}. New York: MIT Press, 2019.

NASA. \t\textit{2020 NASA Technology Taxonomy}. New York: Unknown Publisher, 2020.

NASA. \t\textit{NASA's Plan for Sustained Lunar Exploration and Development}. New York: Unknown Publisher, 2020.

Pyle, Rod. \t\textit{The Future of Space Exploration: Solutions to the Problems}. New York: BenBella Books, 2019.

Wanjek, Christopher. \t\textit{Spacefarers: How Humans Will Settle the Moon, Mars, and Beyond}. New York: Harvard University Press, 2020.

Zubrin, Robert. \t\textit{The Case for Space: How the Revolution in Spaceflight Opens Up a Future of Limitless Possibility}. New York: Unknown Publisher, 2019.

al., Yang Gao et. \t\textit{The grand challenges of space robotics}. New York: IET, 2021.

al., Jekan Thangavelautham et. \t\textit{Space Robotics: A Survey and a Look to the Future}. New York: Johns Hopkins University Press+ORM, 2022.

\end{hangparas}

\cleardoublepage

\vfill
\begin{center}
For more information and to purchase this book, please visit our website:
\par\vspace{1em}
NimbleBooks.com
\end{center}
\cleardoublepage
