\chapter*{Glossary}
\addcontentsline{toc}{chapter}{Glossary}

\textbf{\korean{서예}} \textit{calligraphy}
The art of beautiful handwriting, often practiced alongside pilsa for aesthetic and meditative purposes.
\vspace{12pt}

\textbf{\korean{집중}} \textit{concentration, focus}
The mental state of focused attention achieved through mindful transcription.
\vspace{12pt}

\textbf{\korean{깨달음}} \textit{enlightenment, realization}
Sudden understanding or insight that can arise through contemplative practices like pilsa.
\vspace{12pt}

\textbf{\korean{평정심}} \textit{equanimity, composure}
Mental calmness and composure maintained through mindful practice.
\vspace{12pt}

\textbf{\korean{묵상}} \textit{meditation, contemplation}
Deep reflection and contemplation, often achieved through the practice of pilsa.
\vspace{12pt}

\textbf{\korean{마음챙김}} \textit{mindfulness}
The practice of maintaining moment-to-moment awareness, cultivated through pilsa.
\vspace{12pt}

\textbf{\korean{인내}} \textit{patience, perseverance}
The quality of persistence and patience developed through regular pilsa practice.
\vspace{12pt}

\textbf{\korean{수행}} \textit{practice, cultivation}
Spiritual or mental practice aimed at self-improvement and enlightenment.
\vspace{12pt}

\textbf{\korean{성찰}} \textit{self-reflection, introspection}
The process of examining one's thoughts and actions, facilitated by pilsa practice.
\vspace{12pt}

\textbf{\korean{정성}} \textit{sincerity, devotion}
The heartfelt dedication and care brought to the practice of transcription.
\vspace{12pt}

\textbf{\korean{정신수양}} \textit{spiritual cultivation}
The development of one's spiritual and mental faculties through disciplined practice.
\vspace{12pt}

\textbf{\korean{고요함}} \textit{stillness, tranquility}
The peaceful mental state cultivated through focused transcription practice.
\vspace{12pt}

\textbf{\korean{수련}} \textit{training, discipline}
Regular practice and training to develop skill and spiritual growth.
\vspace{12pt}

\textbf{\korean{필사}} \textit{transcription, copying by hand}
The traditional Korean practice of copying literary texts by hand to improve understanding and mindfulness.
\vspace{12pt}

\textbf{\korean{지혜}} \textit{wisdom}
Deep understanding and insight gained through contemplative study and practice.
\vspace{12pt}
